---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

library(spotlight)
```

# spotlight

[![Travis-CI Build Status](https://travis-ci.org/JohnCoene/spotlight.svg?branch=master)](https://travis-ci.org/JohnCoene/spotlight) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/JohnCoene/spotlight?branch=master&svg=true)](https://ci.appveyor.com/project/JohnCoene/spotlight)

R wrapper to the [DBpedia Spotlight API](http://www.dbpedia-spotlight.org/). All [official documentation](https://github.com/dbpedia-spotlight/dbpedia-spotlight-model) is online.

> It is a tool for automatically annotating mentions of DBpedia resources in text, providing a solution for linking unstructured information sources to the Linked Open Data cloud through DBpedia. -- DBpedia Spotlight

## Installation

You can install spotlight from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("JohnCoene/spotlight")
```

## Example

```{r example}
spot_setup(response = "data.frame") # return data.frame

# Fake data to extract entities from 
data <- data.frame(
  text = c(
    "This text is about France.",
    "This text is about Ecology.",
    "szzza dasdazsd azzsd daawq" # garbage
  )
)

results <- spot(data, text) # get entities

spot_widen(results) # Widen data.frames
```
