---
output: 
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

library(spotlight)
```

# spotlight

[![Travis build status](https://travis-ci.org/news-r/spotlight.svg?branch=master)](https://travis-ci.org/news-r/spotlight) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/JohnCoene/spotlight?branch=master&svg=true)](https://ci.appveyor.com/project/JohnCoene/spotlight)

R wrapper to the [DBpedia Spotlight API](http://www.dbpedia-spotlight.org/). All [official documentation](https://github.com/dbpedia-spotlight/dbpedia-spotlight-model) is online.

> It is a tool for automatically annotating mentions of DBpedia resources in text, providing a solution for linking unstructured information sources to the Linked Open Data cloud through DBpedia. - DBpedia Spotlight

Global options are set with `spot_set_opts`.

## Installation

You can install spotlight from github with:

```r
# install.packages("devtools")
devtools::install_github("news-r/spotlight")
```

## Examples

```{r example}
library(spotlight)

# Data to extract entities from 
text = c(
  "Donald Trump is probably in Washington DC.",
  "szzza dasdazsd azzsd daawq", # garbage
  "" # empty document
)

# remove empty documents
text <- spot_filter(text)

# Annotate
results <- spot_annotate(text)

# Annotate specific types
places <- spot_annotate(text, types = "DBpedia:Place")

knitr::kable(places)
```
